Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-22 paper/current/main.tex
update caption

%
% Figure - SemAxis results
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
	\caption{
		\textbf{Length of organization vectors captures the connection diversity of organizations.}
		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
		The L2 norm corresponds to the distance from the origin of the vector space.
		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
		Uncolored points are universities not listed on a times rank.
		A "boomerang"-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm). 
		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
		The red line is the line of the best fit.
	}
	\label{fig:semaxis}
\end{figure}

>>>>

%
% Figure - SemAxis results
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
	\caption{
		\textbf{Length of organization vectors captures a connection diversity of organizations.}
		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
		The L2 norm corresponds to the distance from the origin of the vector space.
		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
		Uncolored points are universities not listed on a times rank.
		A "boomerang"-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm). 
		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
		The L2 norm is correlated weakly with the number of connections divided by the number of researchers in the organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
		The red line is the line of the best fit.

	}
	\label{fig:semaxis}
\end{figure}
